Rigidity of Expectation Formation: Additional Evidence from Desntify Forecasts

### 2019-06-27 paper/Draft.tex
Improving latex formatting and addressing a few technical issues. use citet instead of cite for line break of aphalike. also ht for tables and charts to adjust the positions.

\documentclass[]{article}
\usepackage{amsmath}
\usepackage{adjustbox}
\usepackage{graphicx}

@@

The potential contribution lies in the extra insights I may get from using probablistic questions.\footnote{For an insightful survey on the importance of measuring subjective expectations using probablistic surveys, see \cite{manski2004measuring}.} One obvious advantage of density expectations compared to point one is availability of higher moments, i.e. variance of the forecast indicates the dispersion of the forecasts. Along time dimension, the dynamics of conditional relative likelihood is a useful indicator of information gain or forecasting efficiency. Besides, as in a typical signal-extraction model, the prediction that new information reduce conditional variance can be tested only using probability distributions. Although the detailed implementation of these tests involves technical difficulties, the ideas are quite clear.  Lastly, with second moments in individual level expectations, we are allowed to potentialy explore the heterogeneity across agents within one theory. For instance, sticky information typically assume a posson update rate for all agents in the economy. This is partly due to the fact that available data only allows us to recover single parameter of regidity instead of inter-group heterogeneity.

@@

$I_{i,t}$ is the information set available for individual $i$ at time t. The information set can be  agent specific, thus it has subscript $i$.  The specific content contained in $I_t$ varies from different models of expectation. For instance, sticky expectation and rational inattention literature all assume that agents are not able to update new information instataneously. So the information set may not contain the most recent realization of the variable of forecast $y_t$. \footnote{Given the same information set available to agents, different theories may also differ in the underlying models each agent use to form the conditional density of the variables by agent $i$. Examples of such include multi-prior or model uncertainty. \cite{xx}. }

@@

The population analogues of individual mean forecast, uncertainty and forecast errors are simply the average of the individual moments taken across agents. Denote them as $\bar y_{t+h|t}$, $\bar \sigma^2_{t+h|t}$, and $\overline{FE}_{t+h|t}$, respectively. Hereafter, they are termed as population mean forecast, population uncertainty and population forecast error, respectively. In addition, disagreements is defined as the cross-sectional variance of mean forecasts of individual agents.  Denote it as $\overline{Var}_{t+h|t}(y_{i,t+h|t}) $. To simplify notation, let us directly call it $\overline{Disg}_{t+h|t}$.  \footnote{This is the same terminology used by \cite{xx}.}

@@

\begin{table}[]\label{MomSum}
	\centering
		\caption{Definition and Notation of Moments}
	\begin{tabular}{ll}

@@

I use supscrit of $*$ to denote all the moments according to FIRE. It is easy to see that the forecast error is orthogonal to information available till time $t$. This provides the a well known null hypothesis of FIRE. \cite{xx}

@@

FIRE also has predictions about  population disagreements. \footnote{For instance, \cite{mankiw2003disagreement} documents substantial time-varying disagreements about future inflation using consumers and professional forecasters' survey. } As agents perfect update the same information, there is no disagreements at any point of the time.

@@

A corollary is that disagreements do not respond to realized shocks any any point of the time.  \footnote{Empricial tests of this kind include \cite{xx}.\cite{xx} etc. }

In addition to forecast error and disagreements, according to FIRE all individual shares the same degree of uncertainty. The uncertainty simply comes from uncertainty about future unrealized shocks between $t$ and $t+h$. To put it another way, according to FIRE, there is neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \cite{}'s terminology.}

@@

The time series behavior of uncertainty according to FIRE is less obvious. Weather it is time-variant depends on if the variance of the shocks $\omega_t$ is time varying. Although in our baseline case we make such an assumption, in general it may not be true. \footnote{\cite{xx} on time-varying volatility.}

@@

The theory of sticky expectation (\cite{xx}, \cite{xx} ), regardless of its different microfoundations by various authors, builds upon the assumption that agents do not update information instantaneously as they do in FIRE. One of the most tractable models assume there is a homogenous Possion rate $\lambda$ of updating among the population. Specificaly, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.

@@

Relying upon the Law of Large Numbers, we can derive testable predictions about population moments that allow us perform tests of sticky expectation and recover rigidity parameter $\lambda$. \footnote{\cite{carroll2003macroeconomic} is one notable example of this.}

One well known prediction from SE literature is that the average foreacast is a weighted average of update-to-date rational expectation and lagged average expectation as reproduced below. \footnote{See \cite{coibion2012can} or appendix of this paper for detailed steps.} It can be also expressed as a weighted average to all the past realizations of $y$. Setting $\lambda=1$, then the SE collapses to FIRE and the average forecast is equal to $y$'s long-run mean of zero.

@@

\cite{coibion2012can} also derives predictions about the disagreements in rigidity models. Unlike zero disagreements in FIRE, SE is characterized by non-zero dispersion in forecasting because of different lags in updating across populations. \footnote{need to check if correct also. Need to derive change in disagreements.}

@@

In SE, disagreements rise after realization of the shock and gradually returns to its steady state level. In the same time, it does not depend upon the particular realization of the shock. \cite{coibion2012can} derive the impulse response of dispersion at time $t+j$ to a shock that realized at $t$.

@@

A class of noisy information models (\cite{},\cite{}) describes the expectation formation as a process of extracting or filtering true variable $y_t$ from a sequence of realized signals. The starting assumption is that agent cannot observe the true variable perfectly. Unlike information rigidity model, it is assumed that agents keep track of the realizations of the signals instantaneously all the time.

@@

\begin{figure}[h]\label{IllustrateNI}
	\centering
	\includegraphics[width=13cm]{figures/ni_illustration.png}  
	\caption{Illustration Noisy Information}
\end{figure}

@@

\begin{figure}[h]\label{ir_pop}
	\centering
	\includegraphics[width=15cm]{figures/ir_popseni.png} 
	\caption{Impulse responses of moments to a shock to inflation}
\end{figure}

@@

\begin{figure}[h]\label{rigidity}
	\centering
	\includegraphics[width=13cm]{figures/rigidity.png} 
	\caption{Rigidity from Two Models}
\end{figure}

@@

\begin{enumerate}
\item Rational inattention. 
\begin{itemize}
	\item Chris Sim's model.\cite{sims2003implications} Information serves the role of uncertainty reduction measured by relative entropy. Agents optimally trade off the fixed cost of being attentative versus the gain from uncertainty gain.   
	\item Ricardo Reis's model. \cite{reis2006inattentive}
	\item Xavier Gabaix's sparse matrix model. \cite{gabaix2014sparsity}
\end{itemize}

\item Epidemiologic view. \cite{carroll2003macroeconomic} Regardless of the microfoundations of the information rigidity, households infrequently get access to more rational-and-up-to-date expectations from professional forecasters with a poisson process.

\item Strategic behaviors. Second order belief, i.e., what you believe of what others believe. \cite{angeletos2009incomplete}

@@

We follow \cite{engelberg2009comparing} to estiamte the density distribution of each individual surveyee for SPF. New York Fed has followed the same procedures for SCE and directly provided their estimate of uncertainty. Therefore, I directly use them.

@@

\begin{table}[]
			\caption{Information of Data}
	\begin{tabular}{lll}

@@

\begin{figure}[h]\label{UnceratitnyOtherMoments}
	\centering
		\centering
	\smallskip
	\includegraphics[width=3.5cm]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
	\includegraphics[width=3.5cm]{figures/SPFCPI_FE_varSPFCPIQ.png}
	\includegraphics[width=3.5cm]{figures/CPI_disg_varSPFCPIQ.png}\\
	\smallskip
	\includegraphics[width=3.5cm]{figures/Inf1yf_PCE_varSPFPCEQ.png}
	\includegraphics[width=3.5cm]{figures/SPFPCE_FE_varSPFPCEQ.png}
	\includegraphics[width=3.5cm]{figures/PCE_disg_varSPFPCEQ.png}\\
	\smallskip	
	\includegraphics[width=3.5cm]{figures/Inf1yf_CPIAU_varSCEM.png}
	\includegraphics[width=3.5cm]{figures/SCE_FE_varSCEM.png}
	\includegraphics[width=3.5cm]{figures/Q9_disg_varSCEM.png}\\
		\caption{Unceratinty and Other Moments}
\end{figure}

\begin{figure}[h]\label{IQR_Unceratitny}
	\centering
	\includegraphics[width=8cm]{figures/IQRvarCPIQ.png} \\
	\smallskip
	\includegraphics[width=8cm]{figures/IQRvarPCEQ.png}\\
		\smallskip
	\includegraphics[width=8cm]{figures/IQRvarSCEM.png}\\
	\caption{Dispersion in Mean Forecast and Unceratinty }
\end{figure}

\begin{figure}[h]\label{Unceratitny_Histogram}
	\centering
	\includegraphics[width=6cm]{figures/PRCCPIMean1_hist.png} 
	\includegraphics[width=6cm]{figures/PRCCPIVar1_hist.png}  \\
	\smallskip
		\includegraphics[width=6cm]{figures/PRCPCEMean1_hist.png} 
	\includegraphics[width=6cm]{figures/PRCPCEVar1_hist.png}  \\
	\smallskip
		\includegraphics[width=6cm]{figures/SCEmean_hist.png} 
	\includegraphics[width=6cm]{figures/SCEvar_hist.png}  \\
	\caption{Distribution of Mean Forecast and Uncertainty }
\end{figure}

\begin{figure}[h]\label{RevisionHist}
	\centering
	\includegraphics[width=6cm]{figures/PRCCPIMean_rv_hist.png} 
	\includegraphics[width=6cm]{figures/PRCCPIVar_rv_hist.png}  \\
	\smallskip
	\includegraphics[width=6cm]{figures/PRCPCEMean_rv_hist.png} 
	\includegraphics[width=6cm]{figures/PRCPCEVar_rv_hist.png}  \\
	\caption{Distribution of Revision in Forecasts}
\end{figure}

@@

In Table \ref{NullTestTable}, I reproduce a number of commonly used tests of null hypothesis of FIRE replying on differnet specific implications discussed in the previous section mostly following \cite{mankiw2003disagreement}.

@@

 The second batch of tests focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \cite{nordhaus1987forecasting} and \cite{fuhrer2018intrinsic}. In particular, I follow the model specifications in \cite{fuhrer2018intrinsic}. According to FIRE, rational forecast revision only responds to newly realized shocks thus it cannot be predicted by past information. For the same reason, regression coefficient of forecast for $y_{t+h}$  at time $t+1$ on that at $t-1$ is exactly equal to $1$, implying one-to-one responses.  A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.

@@

\begin{table}[]\label{NullTestTable}
	\caption{Tests of Rationality and Efficicency using Forecast Errors}
	\centering 
\begin{tabular}{llll}
	\hline 
	& SPF CPI          & SPF PCE          & SCE            \\
	\hline 
	\multicolumn{4}{l}{Test 1: Bias}                                                           \\
	\hline 
	Constant                            & 0.122***         & 0.586***         & 2.220***       \\
	& (0.017)          & (0.061)          & (0.019)        \\
	\hline 
	N                                   & 4697             & 1208             & 67380          \\
	\hline 
	\multicolumn{4}{l}{Test 2: FE depends on past information}                                  \\
	\hline 
	Forecast 1-yr before                & 0.307***         & 0.586***         & NA             \\
	& (0.020)          & (0.061)          & NA             \\
	Constant                            & -0.655***        & -0.777***        & NA             \\
	& (0.060)          & (0.116)          & NA             \\
	\hline 
	N                                   & 3429             & 1208             & NA             \\
	$R^2$                 & 0.0721           & 0.118            & NA             \\
	\hline 
	\multicolumn{4}{l}{Test 3: FEs of non-overlapping forecast horizons are serially correlated} \\
	\hline 
	Forecast Error 1-year before        & 0.0756***        & 0.0503***        & NA             \\
	& (0.020)          & (0.035)          & NA             \\
	Constant                            & 0.145***         & 0.275***         & NA             \\
	& (0.021)          & (0.035)          & NA             \\
	\hline 
	N                                   & 3356             & 1208             & NA             \\
	$R^2$                   & 0.00591          & 0.00264          & NA             \\
	\hline 
	\multicolumn{4}{l}{Test 4: Overlapping FEs are only weakly serially correlated}                          \\
	\hline 
	Forecast Error 1-q before           & 0.657***         & 0.834***         & 0.297***       \\
	& (0.025)          & (0.037)          & (0.021)        \\
	Forecast Error 2-q before           & 0.0282           & -0.0858          & 0.308***       \\
	& (0.027)          & (0.048)          & (0.046)        \\
	Forecast Error 3-q before           & -0.0244          & -0.0555          & 0.311***       \\
	& (0.025)          & (0.038)          & (0.045)        \\
	Constant                            & 0.0626***        & 0.113***         & 0.742***       \\
	& (0.019)          & (0.026)          & (0.097)        \\
	\hline 
	N                                   & 2536             & 1004             & 2836           \\
	$R^2$                & 0.439            & 0.552            & 0.232    \\
	\hline      
\end{tabular}
\end{table}

\newpage

\begin{adjustbox}{angle=90}\label{RevEfficiency}
	\begin{tabular}{lllllllll}
		\hline 
		& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\
		\hline 
		\multicolumn{9}{l}{Test 1.  Revision efficiency of mean forecast}            \\
	                                            \hline 
		& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
		\hline 
		L.InfExp\_Mean\_rv  &               & 0.539***  & 0.418*** & 0.387*** &               & 0.606***  & 0.435***  & 0.369***  \\
		&               & (0.031)   & (0.043)  & (0.052)  &               & (0.034)   & (0.042)   & (0.049)   \\
		L2.InfExp\_Mean\_rv &               &           & 0.218*** & 0.166**  &               &           & 0.261***  & 0.246***  \\
		&               &           & (0.040)  & (0.053)  &               &           & (0.047)   & (0.058)   \\
		L3.InfExp\_Mean\_rv &               &           &          & 0.134**  &               &           &           & 0.116     \\
		&               &           &          & (0.048)  &               &           &           & (0.069)   \\
		SPFCPI\_ct50        &               & -0.444*** & -0.391** & -0.454** &               &           &           &           \\
		&               & (0.105)   & (0.124)  & (0.138)  &               &           &           &           \\
		SPFPCE\_ct50        &               &           &          &          &               & -0.432*** & -0.413*** & -0.504*** \\
		&               &           &          &          &               & (0.109)   & (0.111)   & (0.138)   \\
		& -1.257***     & 0.329     & 0.351    & 0.546*   & -1.095***     & 0.365     & 0.428*    & 0.641**   \\
		Constant & (0.045)       & (0.191)   & (0.237)  & (0.269)  & (0.039)       & (0.188)   & (0.191)   & (0.228)   \\
		\hline 
		N                   & 1337          & 1045      & 822      & 652      & 1111          & 867       & 683       & 549       \\
		$R^2$                  & 0.000         & 0.335     & 0.355    & 0.372    & 0.000         & 0.409     & 0.444     & 0.452     \\
		\hline 
		\multicolumn{9}{l}{Test 2. Revision efficiency of uncertainty}                                                            \\
		\hline 
		& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
		\hline 
		L.InfExp\_Var\_rv   &               & 0.290*    & 0.529*** & 0.581*** &               & 0.577***  & 0.477***  & 0.344*    \\
		&               & (0.122)   & (0.117)  & (0.145)  &               & (0.080)   & (0.130)   & (0.148)   \\
		L2.InfExp\_Var\_rv  &               &           & -0.059   & -0.209   &               &           & 0.360*    & 0.205*    \\
		&               &           & (0.125)  & (0.127)  &               &           & (0.143)   & (0.098)   \\
		L3.InfExp\_Var\_rv  &               &           &          & 0.353**  &               &           &           & 0.390*    \\
		&               &           &          & (0.121)  &               &           &           & (0.149)   \\
		Constant              & -0.034***     & -0.011**  & -0.008*  & -0.005   & -0.039***     & -0.019**  & -0.010**  & -0.007*   \\
		& (0.005)       & (0.004)   & (0.003)  & (0.004)  & (0.006)       & (0.006)   & (0.003)   & (0.003)   \\
		\hline 
		N                   & 1189          & 877       & 663      & 504      & 1082          & 801       & 604       & 458       \\
	$R^2$                 & 0.000         & 0.124     & 0.284    & 0.408    & 0.000         & 0.353     & 0.583     & 0.723    \\
		\hline 
	\end{tabular}
\end{adjustbox}

>>>>

\documentclass[]{article}
\usepackage{amsmath}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage[a4paper,bindingoffset=0.2in,%
left=1in,right=1in,top=1.2in,bottom=1.2in,%
footskip=.25in]{geometry}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=blue,      
	urlcolor=blue,
	citecolor=blue
}
\usepackage{natbib}

@@

The potential contribution lies in the extra insights I may get from using probablistic questions.\footnote{For an insightful survey on the importance of measuring subjective expectations using probablistic surveys, see \citet{manski2004measuring}.} One obvious advantage of density expectations compared to point one is availability of higher moments, i.e. variance of the forecast indicates the dispersion of the forecasts. Along time dimension, the dynamics of conditional relative likelihood is a useful indicator of information gain or forecasting efficiency. Besides, as in a typical signal-extraction model, the prediction that new information reduce conditional variance can be tested only using probability distributions. Although the detailed implementation of these tests involves technical difficulties, the ideas are quite clear.  Lastly, with second moments in individual level expectations, we are allowed to potentialy explore the heterogeneity across agents within one theory. For instance, sticky information typically assume a posson update rate for all agents in the economy. This is partly due to the fact that available data only allows us to recover single parameter of regidity instead of inter-group heterogeneity.

@@

$I_{i,t}$ is the information set available for individual $i$ at time t. The information set can be  agent specific, thus it has subscript $i$.  The specific content contained in $I_t$ varies from different models of expectation. For instance, sticky expectation and rational inattention literature all assume that agents are not able to update new information instataneously. So the information set may not contain the most recent realization of the variable of forecast $y_t$. \footnote{Given the same information set available to agents, different theories may also differ in the underlying models each agent use to form the conditional density of the variables by agent $i$. Examples of such include multi-prior or model uncertainty. \citet{xx}. }

@@

The population analogues of individual mean forecast, uncertainty and forecast errors are simply the average of the individual moments taken across agents. Denote them as $\bar y_{t+h|t}$, $\bar \sigma^2_{t+h|t}$, and $\overline{FE}_{t+h|t}$, respectively. Hereafter, they are termed as population mean forecast, population uncertainty and population forecast error, respectively. In addition, disagreements is defined as the cross-sectional variance of mean forecasts of individual agents.  Denote it as $\overline{Var}_{t+h|t}(y_{i,t+h|t}) $. To simplify notation, let us directly call it $\overline{Disg}_{t+h|t}$.  \footnote{This is the same terminology used by \citet{xx}.}

@@

\begin{table}[]
	\centering
		\caption{Definition and Notation of Moments}
		\label{MomSum}
	\begin{tabular}{ll}

@@

I use supscrit of $*$ to denote all the moments according to FIRE. It is easy to see that the forecast error is orthogonal to information available till time $t$. This provides the a well known null hypothesis of FIRE. \citet{xx}

@@

FIRE also has predictions about  population disagreements. \footnote{For instance, \citet{mankiw2003disagreement} documents substantial time-varying disagreements about future inflation using consumers and professional forecasters' survey. } As agents perfect update the same information, there is no disagreements at any point of the time.

@@

A corollary is that disagreements do not respond to realized shocks any any point of the time.  \footnote{Empricial tests of this kind include \citet{xx}.\citet{xx} etc. }

In addition to forecast error and disagreements, according to FIRE all individual shares the same degree of uncertainty. The uncertainty simply comes from uncertainty about future unrealized shocks between $t$ and $t+h$. To put it another way, according to FIRE, there is neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \citet{}'s terminology.}

@@

The time series behavior of uncertainty according to FIRE is less obvious. Weather it is time-variant depends on if the variance of the shocks $\omega_t$ is time varying. Although in our baseline case we make such an assumption, in general it may not be true. \footnote{\citet{xx} on time-varying volatility.}

@@

The theory of sticky expectation (\citet{xx}, \citet{xx} ), regardless of its different microfoundations by various authors, builds upon the assumption that agents do not update information instantaneously as they do in FIRE. One of the most tractable models assume there is a homogenous Possion rate $\lambda$ of updating among the population. Specificaly, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.

@@

Relying upon the Law of Large Numbers, we can derive testable predictions about population moments that allow us perform tests of sticky expectation and recover rigidity parameter $\lambda$. \footnote{\citet{carroll2003macroeconomic} is one notable example of this.}

One well known prediction from SE literature is that the average foreacast is a weighted average of update-to-date rational expectation and lagged average expectation as reproduced below. \footnote{See \citet{coibion2012can} or appendix of this paper for detailed steps.} It can be also expressed as a weighted average to all the past realizations of $y$. Setting $\lambda=1$, then the SE collapses to FIRE and the average forecast is equal to $y$'s long-run mean of zero.

@@

\citet{coibion2012can} also derives predictions about the disagreements in rigidity models. Unlike zero disagreements in FIRE, SE is characterized by non-zero dispersion in forecasting because of different lags in updating across populations. \footnote{need to check if correct also. Need to derive change in disagreements.}

@@

In SE, disagreements rise after realization of the shock and gradually returns to its steady state level. In the same time, it does not depend upon the particular realization of the shock. \citet{coibion2012can} derive the impulse response of dispersion at time $t+j$ to a shock that realized at $t$.

@@

A class of noisy information models (\citet{},\citet{}) describes the expectation formation as a process of extracting or filtering true variable $y_t$ from a sequence of realized signals. The starting assumption is that agent cannot observe the true variable perfectly. Unlike information rigidity model, it is assumed that agents keep track of the realizations of the signals instantaneously all the time.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=13cm]{figures/ni_illustration.png}  
	\caption{Nowcasting and Forecasting in Noisy Information}
	\label{IllustrateNI}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=16cm]{figures/ir_popseni.png} 
	\caption{Impulse responses of moments to a shock to inflation}
	\label{ir_pop}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=13cm]{figures/rigidity.png} 
	\caption{Rigidity from Two Models}
	\label{rigidity}
\end{figure}

@@

\begin{enumerate}
\item Rational inattention. 
\begin{itemize}
	\item Chris Sim's model.\citet{sims2003implications} Information serves the role of uncertainty reduction measured by relative entropy. Agents optimally trade off the fixed cost of being attentative versus the gain from uncertainty gain.   
	\item Ricardo Reis's model. \citet{reis2006inattentive}
	\item Xavier Gabaix's sparse matrix model. \citet{gabaix2014sparsity}
\end{itemize}

\item Epidemiologic view. \citet{carroll2003macroeconomic} Regardless of the microfoundations of the information rigidity, households infrequently get access to more rational-and-up-to-date expectations from professional forecasters with a poisson process.

\item Strategic behaviors. Second order belief, i.e., what you believe of what others believe. \citet{angeletos2009incomplete}

@@

We follow \citet{engelberg2009comparing} to estiamte the density distribution of each individual surveyee for SPF. New York Fed has followed the same procedures for SCE and directly provided their estimate of uncertainty. Therefore, I directly use them.

@@

\begin{table}[ht]
			\caption{Information of Data}
			\label{DataInfo}
	\begin{tabular}{lll}

@@

\begin{figure}[ht]
	\centering
	\smallskip
	\includegraphics[width=4.5cm]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
	\includegraphics[width=4.5cm]{figures/SPFCPI_FE_varSPFCPIQ.png}
	\includegraphics[width=4.5cm]{figures/CPI_disg_varSPFCPIQ.png}\\
	\smallskip
	\includegraphics[width=4.5cm]{figures/Inf1yf_PCE_varSPFPCEQ.png}
	\includegraphics[width=4.5cm]{figures/SPFPCE_FE_varSPFPCEQ.png}
	\includegraphics[width=4.5cm]{figures/PCE_disg_varSPFPCEQ.png}\\
	\smallskip	
	\includegraphics[width=4.5cm]{figures/Inf1yf_CPIAU_varSCEM.png}
	\includegraphics[width=4.5cm]{figures/SCE_FE_varSCEM.png}
	\includegraphics[width=4.5cm]{figures/Q9_disg_varSCEM.png}\\
		\caption{Unceratinty and Other Moments}
		\label{UnceratitnyOtherMoments}
\end{figure}

\begin{figure}[ht]
	\centering
	\includegraphics[width=8cm]{figures/IQRvarCPIQ.png} \\
	\smallskip
	\includegraphics[width=8cm]{figures/IQRvarPCEQ.png}\\
		\smallskip
	\includegraphics[width=8cm]{figures/IQRvarSCEM.png}\\
	\caption{Dispersion in Mean Forecast and Unceratinty }
	\label{IQR_Unceratitny}
\end{figure}

\begin{figure}[ht]
	\centering
	\includegraphics[width=7cm]{figures/PRCCPIMean1_hist.png} 
	\includegraphics[width=7cm]{figures/PRCCPIVar1_hist.png}  \\
	\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEMean1_hist.png} 
	\includegraphics[width=7cm]{figures/PRCPCEVar1_hist.png}  \\
	\smallskip
		\includegraphics[width=7cm]{figures/SCEmean_hist.png} 
	\includegraphics[width=7cm]{figures/SCEvar_hist.png}  \\
	\caption{Distribution of Mean Forecast and Uncertainty }
	\label{Unceratitny_Histogram}
\end{figure}

\begin{figure}[ht]
	\centering
	\includegraphics[width=7cm]{figures/PRCCPIMean_rv_hist.png} 
	\includegraphics[width=7cm]{figures/PRCCPIVar_rv_hist.png}  \\
	\smallskip
	\includegraphics[width=7cm]{figures/PRCPCEMean_rv_hist.png} 
	\includegraphics[width=7cm]{figures/PRCPCEVar_rv_hist.png}  \\
	\caption{Distribution of Revision in Forecasts}
	\label{RevisionHist}
\end{figure}

@@

In Table \ref{NullTestTable}, I reproduce a number of commonly used tests of null hypothesis of FIRE replying on differnet specific implications discussed in the previous section mostly following \citet{mankiw2003disagreement}.

@@

\begin{table}[ht]
	\caption{Tests of Rationality and Efficicency using Forecast Errors}
	\label{NullTestTable}
	\centering 
\begin{tabular}{llll}
	\hline 
	& SPF CPI          & SPF PCE          & SCE            \\
	\hline 
	\multicolumn{4}{l}{Test 1: Bias}                                                           \\
	\hline 
	Constant                            & 0.122***         & 0.586***         & 2.220***       \\
	& (0.017)          & (0.061)          & (0.019)        \\
	\hline 
	N                                   & 4697             & 1208             & 67380          \\
	\hline 
	\multicolumn{4}{l}{Test 2: FE depends on past information}                                  \\
	\hline 
	Forecast 1-yr before                & 0.307***         & 0.586***         & NA             \\
	& (0.020)          & (0.061)          & NA             \\
	Constant                            & -0.655***        & -0.777***        & NA             \\
	& (0.060)          & (0.116)          & NA             \\
	\hline 
	N                                   & 3429             & 1208             & NA             \\
	$R^2$                 & 0.0721           & 0.118            & NA             \\
	\hline 
	\multicolumn{4}{l}{Test 3: FEs of non-overlapping forecast horizons are serially correlated} \\
	\hline 
	Forecast Error 1-year before        & 0.0756***        & 0.0503***        & NA             \\
	& (0.020)          & (0.035)          & NA             \\
	Constant                            & 0.145***         & 0.275***         & NA             \\
	& (0.021)          & (0.035)          & NA             \\
	\hline 
	N                                   & 3356             & 1208             & NA             \\
	$R^2$                   & 0.00591          & 0.00264          & NA             \\
	\hline 
	\multicolumn{4}{l}{Test 4: Overlapping FEs are only weakly serially correlated}                          \\
	\hline 
	Forecast Error 1-q before           & 0.657***         & 0.834***         & 0.297***       \\
	& (0.025)          & (0.037)          & (0.021)        \\
	Forecast Error 2-q before           & 0.0282           & -0.0858          & 0.308***       \\
	& (0.027)          & (0.048)          & (0.046)        \\
	Forecast Error 3-q before           & -0.0244          & -0.0555          & 0.311***       \\
	& (0.025)          & (0.038)          & (0.045)        \\
	Constant                            & 0.0626***        & 0.113***         & 0.742***       \\
	& (0.019)          & (0.026)          & (0.097)        \\
	\hline 
	N                                   & 2536             & 1004             & 2836           \\
	$R^2$                & 0.439            & 0.552            & 0.232    \\
	\hline      
\end{tabular}
\end{table}

The second batch of tests in Table \ref{RevEfficiency} focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \citet{nordhaus1987forecasting} and \citet{fuhrer2018intrinsic}. In particular, I follow the model specifications in \citet{fuhrer2018intrinsic}. According to FIRE, rational forecast revision only responds to newly realized shocks thus it cannot be predicted by past information. For the same reason, regression coefficient of forecast for $y_{t+h}$  at time $t+1$ on that at $t-1$ is exactly equal to $1$, implying one-to-one responses.  A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.

\begin{table}[ht]
	\caption{Tests of Revision Efficiency using Mean Revision and Uncertainty}
	\label{RevEfficency}
\begin{adjustbox}{angle=90}

	\begin{tabular}{lllllllll}
		\hline 
		& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\
		\hline 
		\multicolumn{9}{l}{Test 1.  Revision efficiency of mean forecast}            \\
	                                            \hline 
		& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
		\hline 
		L.InfExp\_Mean\_rv  &               & 0.539***  & 0.418*** & 0.387*** &               & 0.606***  & 0.435***  & 0.369***  \\
		&               & (0.031)   & (0.043)  & (0.052)  &               & (0.034)   & (0.042)   & (0.049)   \\
		L2.InfExp\_Mean\_rv &               &           & 0.218*** & 0.166**  &               &           & 0.261***  & 0.246***  \\
		&               &           & (0.040)  & (0.053)  &               &           & (0.047)   & (0.058)   \\
		L3.InfExp\_Mean\_rv &               &           &          & 0.134**  &               &           &           & 0.116     \\
		&               &           &          & (0.048)  &               &           &           & (0.069)   \\
		SPFCPI\_ct50        &               & -0.444*** & -0.391** & -0.454** &               &           &           &           \\
		&               & (0.105)   & (0.124)  & (0.138)  &               &           &           &           \\
		SPFPCE\_ct50        &               &           &          &          &               & -0.432*** & -0.413*** & -0.504*** \\
		&               &           &          &          &               & (0.109)   & (0.111)   & (0.138)   \\
		& -1.257***     & 0.329     & 0.351    & 0.546*   & -1.095***     & 0.365     & 0.428*    & 0.641**   \\
		Constant & (0.045)       & (0.191)   & (0.237)  & (0.269)  & (0.039)       & (0.188)   & (0.191)   & (0.228)   \\
		\hline 
		N                   & 1337          & 1045      & 822      & 652      & 1111          & 867       & 683       & 549       \\
		$R^2$                  & 0.000         & 0.335     & 0.355    & 0.372    & 0.000         & 0.409     & 0.444     & 0.452     \\
		\hline 
		\multicolumn{9}{l}{Test 2. Revision efficiency of uncertainty}                                                            \\
		\hline 
		& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
		\hline 
		L.InfExp\_Var\_rv   &               & 0.290*    & 0.529*** & 0.581*** &               & 0.577***  & 0.477***  & 0.344*    \\
		&               & (0.122)   & (0.117)  & (0.145)  &               & (0.080)   & (0.130)   & (0.148)   \\
		L2.InfExp\_Var\_rv  &               &           & -0.059   & -0.209   &               &           & 0.360*    & 0.205*    \\
		&               &           & (0.125)  & (0.127)  &               &           & (0.143)   & (0.098)   \\
		L3.InfExp\_Var\_rv  &               &           &          & 0.353**  &               &           &           & 0.390*    \\
		&               &           &          & (0.121)  &               &           &           & (0.149)   \\
		Constant              & -0.034***     & -0.011**  & -0.008*  & -0.005   & -0.039***     & -0.019**  & -0.010**  & -0.007*   \\
		& (0.005)       & (0.004)   & (0.003)  & (0.004)  & (0.006)       & (0.006)   & (0.003)   & (0.003)   \\
		\hline 
		N                   & 1189          & 877       & 663      & 504      & 1082          & 801       & 604       & 458       \\
	$R^2$                 & 0.000         & 0.124     & 0.284    & 0.408    & 0.000         & 0.353     & 0.583     & 0.723    \\
		\hline 
	\end{tabular}
\end{adjustbox}
\end{table}

@@

\begin{table}
	\centering 
	\caption{Weak Tests of Revision Efficiency using Change in Foreacsts and Uncertainty}
	\label{WeakRevEfficiency}
\begin{adjustbox}{width={24cm},totalheight={14cm},angle=90}
	\begin{tabular}{llllllllllllll}
		\hline 
		& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       &                      & \multicolumn{4}{l}{SCE}                           \\
		\hline 
		\multicolumn{14}{l}{Test 3. Weak revision efficiency of change in forecast}                                                                                                                                    \\
		\hline 
		& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
		\hline 
		L.InfExp\_Mean\_ch   &             & -0.295*** & -0.344*** & -0.367*** &               & -0.303*** & -0.348*** & -0.364*** & L.InfExp\_Mean\_ch  &         & -0.433*** & -0.586*** & -0.642*** \\
		&             & (0.034)   & (0.044)   & (0.045)   &               & (0.043)   & (0.059)   & (0.062)   &                    &         & (0.01)     & (0.013)    & (0.025)    \\
